Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-05-18 paper.tex
Fixing some math mode build errors.

% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2016} with
% \usepackage[nohyperref]{icml2016} above.
\usepackage{amsmath}
\usepackage{hyperref}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
\DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays
\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
\DeclareMathOperator{\argmax}{argmax} % no space, limits underneath in displays

@@

\begin{table}[H]
  \begin{tabular}{rl}\toprule
  Program$\to$&Command; $\cdots$; Command\\
  Command$\to$&\texttt{circle}(Expression,Expression)\\
  Command$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
  Command$\to$&\texttt{line}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
  Command$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ if }$(\text{Var} > 0)$\texttt{ \{ }Program\texttt{ \}; }Program\texttt{ \}}\\
  Command$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
  Expression$\to$&\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}\\
  Var$\to$&A free (unused) variable\\
  \mathcal{Z}$\to$&an integer\\
  Axis$\to$&\texttt{X = }\mathcal{Z}\\
  Axis$\to$&\texttt{Y = }\mathcal{Z}\\\bottomrule
  \end{tabular}
  \caption{Grammar over graphics programs. We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}\label{DSL}
\end{table}

>>>>

% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2016} with
% \usepackage[nohyperref]{icml2016} above.
\usepackage{amsmath}
\usepackage{hyperref}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
% \DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays
\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
% \DeclareMathOperator{\argmax}{argmax} % no space, limits underneath in displays

@@

\begin{table}[H]
  \begin{tabular}{rl}\toprule
  Program$\to$&Command; $\cdots$; Command\\
  Command$\to$&\texttt{circle}(Expression,Expression)\\
  Command$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
  Command$\to$&\texttt{line}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
  Command$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ if }$(\text{Var} > 0)$\texttt{ \{ }Program\texttt{ \}; }Program\texttt{ \}}\\
  Command$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
  Expression$\to$&$\mathcal{Z}$\texttt{ * }Var\texttt{ + }$\mathcal{Z}$\\
  Var$\to$&A free (unused) variable\\
  $\mathcal{Z}$$\to$&an integer\\
  Axis$\to$&\texttt{X = }$\mathcal{Z}$\\
  Axis$\to$&\texttt{Y = }$\mathcal{Z}$\\\bottomrule
  \end{tabular}
  \caption{Grammar over graphics programs. We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathcal{Z}$\texttt{ * }Var\texttt{ + }$\mathcal{Z}$).}\label{DSL}
\end{table}
